---
title: "Statistical learning on Mice moverment"
output: 
    pdf_document:
      toc: TRUE
      number_sections: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE) # global setting 
knitr::clean_cache()
 library(readxl)
 library(stringr)
 library(ggplot2)
 library(gganimate)
 library(lubridate)
 library(tidyverse)
 library(plotly)
 library(circular)
 library(tree)       ### 2D
 library(rpart.plot) ### 3D
 library(plotmo)
 library(dplyr)
 library(caret)
```
# ML progect introduction
This progect is on animal behavior analysis. The data was retrieved form Catwalk videos which is coordinates of head, centre and tail of a mouse while on gait analysis. An weight-independent variable, $\theta$, was firt introduced into gait analysis. This proof-of-concept project is going to apply relevent variables into machine learning algorithm. The aims are for classification of treatment groups.


## Outline of the proccess
1. Importing data
  * all.mice
  * 
2. Calculate the rotating angle, **$\theta$**
  * Ploting the data
3. Models bulding
  * Supervised models 
    * Linear regression
      * Validate coeficients (t-test)
      * Validate the model ($R^2$, correlation, F-test)
    * Multiple regression
    * k-nesrest neighor
    * Desicion tree

## Importing data
* The data with coordinates were imported into R.
  * all.mice (function : read.excel.sheet() )
* The calculation of the $\theta$ 
  * all.mice with theta.T, theta.C (function : angle.calculation.tail() )
* The average velocity, theta and variety of theta
  * vel.all.micev: 
   mean velocity and mad.Y in head, centre and tail. 
   mean and var of theta.C and theta.T.
* The interval velocity
  * all.vel.summary:
  vel, mad.Y, in.t (in head, centre and tail)

## all.mice
```{r import, echo=FALSE, message=FALSE}
# function for import

read.excel.sheet <- function(filename){
  names.sht <- excel_sheets(filename)
  for(i in 1:length(names.sht)) 
  { 
    ifelse(i==1,T <- read_excel(filename,sheet = 1), T )
    ifelse(i+1 <= length(names.sht),T2 <- as.data.frame(read_excel(filename,sheet = i+1)),next())
    T  <- rbind.data.frame(T,T2)
  }
  return(T)
}

all.mice <-read.excel.sheet('NPCTG.xlsx')

all.mice <- all.mice %>% rename(c('ID.RUN'='ID'))

all.mice <- all.mice %>% 
  mutate(
    Run= str_extract(all.mice$ID.RUN,'RUN[0-9]+'),
    ID= str_extract(all.mice$ID.RUN,'[A-Z]{4,5}[0-9]{3}\\.[0-9][a-z]'),
    Group= str_extract(all.mice$ID.RUN,'^[A-Z]+')
  )
all.mice <- all.mice %>% select(ID,Group,Run,ID.RUN,everything())
knitr::kable(head(all.mice))
```

## all.mice with theta 
```{r theta  , echo=FALSE,message=FALSE}
angle.calculation.tail <- function(filename1){

  Head <-   filter(filename1, Point == 'Head')
  Centre <- filter(filename1, Point == "Centre")
  Tail <-   filter(filename1, Point == "Tail")
  
  calculation <- Head %>% select(ID.RUN,ID,Run,Group)
  
  calculation <- calculation %>% 
    mutate(
      X.tail.head = Head$X-Tail$X,
      X.cent.head = Head$X-Centre$X,
      
      Y.tail.head = Head$Y-Tail$Y,
      Y.cent.head = Head$Y-Centre$Y,
      
      X.tail.horizontal = Head$X-Tail$X,
      X.cent.horizontal = Head$X-Centre$X,
      horizontal.Y = 0
      )
  
  calculation <- calculation %>% 
    mutate(
      Tail.angel =sign(Head$Y-Tail$Y)*180*(acos(calculation$X.tail.head * calculation$X.tail.horizontal /abs(calculation$X.tail.horizontal) / sqrt((calculation$X.tail.head)^2+(calculation$Y.tail.head)^2)))/(pi),
      Centre.angel=sign(Head$Y-Centre$Y)*180*(acos(calculation$X.cent.head * calculation$X.cent.horizontal /abs(calculation$X.cent.horizontal) / sqrt((calculation$X.cent.head)^2+(calculation$ Y.cent.head)^2)))/(pi)
    )
  
  Pts <- c('Head','Centre','Tail')
  T2 <- data.frame()
  for (i in Pts) {
    T <- as.data.frame(eval(parse(text=i)))
    T <- T %>% 
      mutate(
        Tail.theta = calculation$Tail.angel,
        Centre.theta = calculation$Centre.angel
      )
   ifelse(i=='Head',T2 <- T,T2 <- rbind(T2,T))
  }
 T2 <- T2 %>% mutate(
      theta.T = circular(rad(T2$Tail.theta),type='direction'),
    theta.C = circular(rad(T2$Centre.theta),type='direction')
 )
 #  
  return(T2)
  
}
all.mice <- angle.calculation.tail(all.mice)
knitr::kable(head(all.mice))
```

## vel.all.mice (summary of each run)
```{r average.velocity,echo=FALSE,message=FALSE,warning=FALSE}
Average.velocity <- function(filename2){
  points <- c('Head','Centre','Tail')
  for (i in points) {
    T <-filename2 %>% filter(Point==i) %>% 
      group_by(Group,ID,Run) %>% 
      dplyr::summarise(Xstart=X[which(t==0)],
                       Ystart=Y[which(t==0)],
                       Xend = X[which(t==max(t))],
                       Yend = Y[which(t==max(t))],
                       mean.velocity= abs(Xstart-Xend)/max(t),
                       madY = median(abs(Y)),
                       t = max(t),
                       Point=i,
                       mean.angle.C= mean.circular(abs(theta.C), na.rm=TRUE),
                       mean.angle.T= mean.circular(abs(theta.T), na.rm=TRUE),
                       var.angle.C = var.circular(abs(theta.C), na.rm=TRUE),
                       var.angle.T = var.circular(abs(theta.T), na.rm=TRUE)
                       
                        )
   
        ifelse(i=='Head',all <- T,all <- rbind(all,T))
   
     
  }
  
  return(all %>% 
  dplyr::select(ID,Run,
         Group,Point,
         mean.velocity,
         madY,mean.angle.C,
         mean.angle.T,var.angle.C,
         var.angle.T)
  )
  
}

Vel.all.mice <- Average.velocity(all.mice)
knitr::kable(head(Vel.all.mice))
```

## all.vel.mice (vel in certain interval)

```{r interal velocity, echo=FALSE,message=FALSE,warning=FALSE}
ex <- function(filename,run,number.of.window=10){
  Pts <- c('Head','Centre','Tail')
  d3 <- data.frame()
  d4 <- data.frame()
  for (j in Pts) {
  # uni.run <- unique(all.mice$Run[which(all.mice$ID==filename)])
  d0 <- all.mice %>% filter(ID==filename,Point==j,Run==run)
  N.cell <- ceiling((max(d0$X)-min(d0$X))/number.of.window)
  # N.cell <- ceiling(max(d0$X)/1)
  CUT <- cut(d0$X,N.cell,labels = 1:N.cell)
  d0 <- cbind(d0,CUT)
  CUT1 <- unique(d0$CUT)
  d2 <- data.frame()
  
  for (i in 1:length(CUT1)) {
    d1 <- d0 %>% filter(CUT==CUT1[i])
    d3 <- d1 %>% dplyr::summarise(
      vel= unique(sqrt(max(X)-min(X))^2+(max(Y[which(X==max(X))])-min(Y[which(X==min(X))]))^2)/(max(t)-min(t)),
      mad.Y = mad(Y),
      in.t = max(t)-min(t),
      Point=j,
      # mad.ang = mad(theta)
    )
    ifelse(d3$in.t==0,next(),d2 <- rbind(d2,d3)) 
  }
  d4 <- rbind(d4,d2)
  }
  
  return(d4)
}
ex2 <- function(filename){
  uni.run <- unique(all.mice$Run[which(all.mice$ID==filename)] )
  # leng.run <- length(uni.run)
  dd1 <- data.frame()
  for (i in uni.run) {
    dd0 <- ex(filename,i)
    dd1 <- rbind(dd1,dd0)
  }
  return(dd1)
}

ex3 <- function(filename){
  ID <- unique(filename$ID)
  dd1 <- data.frame()
  for (i in ID) {
    dd0 <- ex2(i)
    dd0 <- dd0 %>% mutate(Group= str_extract(i,'^[A-Z]+'),
                          ID= i)
    dd1 <- rbind(dd1,dd0)
  }
  return(dd1)
}

all.vel.summary <- ex3(all.mice)
knitr::kable(head(all.vel.summary))
```

# Plotting 
## all.mice
### theta.C

```{r theta.C plotting, echo=FALSE,warning=FALSE}
all.mice %>% 
  ggplot(aes(Group,theta.C))+
  geom_boxplot(aes(fill=Group),alpha=1/2)+
  theme_bw()+
  NULL
all.mice %>% na.omit() %>% 
  ggplot(aes(Group,theta.C))+
  geom_boxplot(aes(fill=ID),alpha=1/2)+
  theme_bw()+
  NULL
```
### theta.T

```{r theta.T plotting, echo=FALSE,warning=FALSE}
all.mice %>% 
  ggplot(aes(Group,theta.T))+
  geom_boxplot(aes(fill=Group),alpha=1/2)+
  # geom_point(aes(color=ID),alpha=1/10)+
  # facet_wrap(~Group)+
  theme_bw()+
  NULL

all.mice %>% 
  ggplot(aes(Group,theta.T))+
  geom_boxplot(aes(fill=ID),alpha=1/2)+
  # geom_point(aes(color=ID),alpha=1/10)+
  # facet_wrap(~Group)+
  theme_bw()+
  NULL
```

## theta.C against theta.T

```{r theta.C against theta.T, echo=FALSE,warning=FALSE}
all.mice %>% 
  ggplot(aes(theta.C,theta.T))+
  # geom_boxplot(aes(fill=ID),alpha=1/2)+
  geom_point(aes(color=ID),alpha=1/10)+
  coord_fixed(ratio=1)+
  # facet_wrap(~Group)+
  theme_bw()+
  NULL 

```

## Vel.all.mice (each run)

### mean velocity and madY

```{r mean.velocity AND madY, echo=FALSE,warning=FALSE}
Vel.all.mice %>% 
  ggplot(aes(Point,mean.velocity))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  facet_wrap(~Group)+
  theme_bw()+
  NULL
Vel.all.mice %>% 
  ggplot(aes(Point,madY))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  facet_wrap(~Group)+
  theme_bw()+
  NULL
```

### mean angle in centre and tail

```{r mean.angle.C AND mean.angle.T , echo=FALSE,warning=FALSE}
Vel.all.mice %>% 
  ggplot(aes(Group,mean.angle.C))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  # facet_wrap(~Group)+
  theme_bw()+
  NULL
Vel.all.mice %>% 
  ggplot(aes(Group,mean.angle.T))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  # facet_wrap(~Group)+
  theme_bw()+
  NULL
```

### variety angle centre and tail

```{r var.angle.C AND var.angle.T, echo=FALSE,warning=FALSE}
Vel.all.mice %>% 
  ggplot(aes(Group,var.angle.C))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  # facet_wrap(~Group)+
  theme_bw()+
  NULL
Vel.all.mice %>% 
  ggplot(aes(Group,var.angle.T))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  # facet_wrap(~Group)+
  theme_bw()+
  NULL
```

## all.mice.summary 

### velocity, mad.Y and in.t 

```{r all.mice.summary velocity, mad.Y and in.t, echo=FALSE,warning=FALSE}
all.vel.summary %>% 
  # filter(Group=='WTUT')%>%  
  ggplot(aes(Point,vel))+
  coord_cartesian(ylim = c(0,1000))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  facet_wrap(~Group)+
  theme_bw()+
NULL
all.vel.summary %>% 
  # filter(Group=='WTUT')%>%  
  ggplot(aes(Point,mad.Y))+
  # coord_cartesian(ylim = c(0,1000))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  facet_wrap(~Group)+
  theme_bw()+
NULL
all.vel.summary %>% 
  # filter(Group=='WTUT')%>%  
  ggplot(aes(Point,in.t))+
  # coord_cartesian(ylim = c(0,1000))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  facet_wrap(~Group)+
  theme_bw()+
NULL
```

