---
title: "Update"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
 library(forecast)
 library(readxl)
 library(stringr)
 library(ggplot2)
 library(gganimate)
 library(lubridate)
 library(tidyverse)
 library(plotly)
 library(circular)
 library(tree)       ### 2D
 library(rpart.plot) ### 3D
 library(plotmo)
 library(dplyr)
 library(caret)
# function1 : read excel
read.excel.sheet <- function(filename){
  names.sht <- excel_sheets(filename)
  for(i in 1:length(names.sht)) 
  { 
    if(i==1) T <- read_excel(filename,sheet = 1)
    if(i+1 <= length(names.sht)) T2 <- read_excel(filename,sheet = i+1)
    T  <- rbind(T,T2)
  }
  return(T)
}
# function2 : angle calculation
angle.calculation.tail <- function(filename1){

  Head <-   filter(filename1, Point == 'Head')
  Centre <- filter(filename1, Point == "Centre")
  Tail <-   filter(filename1, Point == "Tail")
  
  calculation <- Head %>% select(ID.RUN,ID,Run,Group,Point)
  
  calculation <- calculation %>% 
    mutate(
      X.tail.head = Head$X-Tail$X,
      X.cent.head = Head$X-Centre$X,
      
      Y.tail.head = Head$Y-Tail$Y,
      Y.cent.head = Head$Y-Centre$Y,
      
      X.tail.horizontal = Head$X-Tail$X,
      X.cent.horizontal = Head$X-Centre$X,
      horizontal.Y = 0
      )
  
  calculation <- calculation %>% 
    mutate(
      Tail.angel =sign(Head$Y-Tail$Y)*180*(acos(calculation$X.tail.head * calculation$X.tail.horizontal /abs(calculation$X.tail.horizontal) / sqrt((calculation$X.tail.head)^2+(calculation$Y.tail.head)^2)))/(pi),
      Centre.angel=sign(Head$Y-Centre$Y)*180*(acos(calculation$X.cent.head * calculation$X.cent.horizontal /abs(calculation$X.cent.horizontal) / sqrt((calculation$X.cent.head)^2+(calculation$ Y.cent.head)^2)))/(pi)
    )
   calculation <- calculation %>% select(-ID.RUN,-ID,-Run,-Group,-Point)
  return(calculation)
  
}

#function3 : average velocity calculation
Average.velocity <- function(filename2){
  ungroup(filename2)
  points <- c('Head','Centre','Tail')
  for (i in points) {
    T <-filename2 %>% 
      group_by(Group,ID,Run) %>%
      filter(Point==i) %>% 
          dplyr::summarise(Xstart=X[which(t==0)],
                       Ystart=Y[which(t==0)],
                       Xend = X[which(t==max(t))],
                       Yend = Y[which(t==max(t))],
                       mean.velocity= abs(Xstart-Xend)/max(t),
                       madY = median(abs(Y)),
                       t = max(t),
                       Point=i,
                       mean.angle.C= mean.circular(abs(theta.C), na.rm=TRUE),
                       mean.angle.T= mean.circular(abs(theta.T), na.rm=TRUE),
                       var.angle.C = var.circular(abs(theta.C), na.rm=TRUE),
                       var.angle.T = var.circular(abs(theta.T), na.rm=TRUE)
                       # mean.angle = mean.circular(CircAngle, na.rm=TRUE),
                       # var.angle = var.circular(CircAngle, na.rm=TRUE)
                        )
   
        ifelse(i=='Head',all <- T,all <- rbind(all,T))
   
     
  }
  return(all %>% 
  dplyr::select(ID,Run,
         Group,Point,
         mean.velocity,
         madY,mean.angle.C,
         mean.angle.T,var.angle.C,
         var.angle.T)
  )
  
}

#function4 : segment time velocity
ex.t <- function(filename,run){
  Pts <- c('Head','Centre','Tail')
  d3 <- data.frame()
  d4 <- data.frame()
  for (j in Pts) {
    # uni.run <- unique(all.mice$Run[which(all.mice$ID==filename)])
    d0 <- all.mice %>% filter(ID==filename,Point==j,Run==run)
    N.cell <- round(max(d0$t)/0.1)
    # N.cell <- ceiling(max(d0$X)/1)
    CUT <- cut(d0$t,N.cell,labels = 1:N.cell)
    d0 <- cbind(d0,CUT)
    CUT1 <- unique(d0$CUT)
    d2 <- data.frame()
    
    for (i in 1:length(CUT1)) {
      d1 <- d0 %>% filter(CUT==CUT1[i])
      d3 <- d1 %>% dplyr::summarise(
        vel= unique(sqrt(max(X)-min(X))^2+(max(Y[which(X==max(X))])-min(Y[which(X==min(X))]))^2)/(max(t)-min(t)),
        mad.Y = mad(Y),
        in.t = max(t)-min(t),
        Point=j,
        # mad.ang = mad(theta)
      )
      d2 <- rbind(d2,d3)
    }
    d4 <- rbind(d4,d2)
    
  }
  
  return(d4)
}
ex2 <- function(filename){
  uni.run <- unique(all.mice$Run[which(all.mice$ID==filename)] )
  # leng.run <- length(uni.run)
  dd1 <- data.frame()
  for (i in uni.run) {
    dd0 <- ex.t(filename,i)
    dd0 <- dd0 %>% mutate(Run=i)
    dd1 <- rbind(dd1,dd0)
  }
  return(dd1)
}
ex3 <- function(filename){
  ID <- unique(filename$ID)
  dd1 <- data.frame()
  for (i in ID) {
    dd0 <- ex2(i)
    dd0 <- dd0 %>% mutate(Group= str_extract(i,'^[A-Z]+'),
                          ID= i)
    dd1 <- rbind(dd1,dd0)
  }
  return(dd1)
}



```


# Behavior analysis update
## 1. Tranditional analysis (descriptive analysis)
### Data sets definition 
#### 1. all.mice : import data from xls
```{r,cache=T}
all.mice <- read.excel.sheet('NPCTG1.xlsx')
all.mice <- all.mice %>% rename(c('ID.RUN'='ID'))
all.mice <- all.mice %>% 
  mutate(
    Run= str_extract(all.mice$ID.RUN,'RUN[0-9]+'),
    ID= str_extract(all.mice$ID.RUN,'[A-Z]{4,5}[0-9]{3}\\.[0-9][a-z]'),
    Group= str_extract(all.mice$ID.RUN,'^[A-Z]+')
  )
all.mice %>% select(ID,Group,Run,ID.RUN,everything())
knitr::kable(head(all.mice),caption='Raw data')
```


#### 2. all.mice.theta : angle calculation
```{r}
all.mice.theta <- angle.calculation.tail(all.mice)
test.h <- cbind(all.mice[which(all.mice$Point=='Head'),],all.mice.theta)
test.c <- cbind(all.mice[which(all.mice$Point=='Centre'),],all.mice.theta)
test.t <- cbind(all.mice[which(all.mice$Point=='Tail'),],all.mice.theta)
all.mice.theta <- rbind(test.h,test.c,test.t)
all.mice.theta <- all.mice.theta %>% mutate(
       theta.T = circular(rad(all.mice.theta$Tail.angel),type='direction'),
       theta.C = circular(rad(all.mice.theta$Centre.angel),type='direction'))
all.mice.theta <- all.mice.theta %>% select(-X.cent.head,-Y.tail.head,-X.tail.head,-Y.cent.head,-X.tail.horizontal,-X.cent.horizontal,-horizontal.Y)

knitr::kable(head(all.mice.theta),caption='Raw data with rotating angle (theta)')
```
#### 3. all.mice.average.vel : average velocity each run calculation
```{r, cache=T}
all.mice.average.vel <- Average.velocity(all.mice.theta)
knitr::kable(head(all.mice.average.vel),caption='each run velocit')

```

#### 4. all.mice.segment.vel : 
```{r, cache=T}
all.mice.segment.vel <- drop_na(ex3(all.mice))
knitr::kable(head(all.mice.segment.vel),caption='velocity in segments')
```

### Graphs 
#### 1.all.mice

```{r, cache=T}
all.mice %>%
  #filter(Point=='Head') %>% 
  ggplot(aes(x=X,y=Y,colour=ID))+
  #geom_point()+
  # geom_path()+
  # geom_point(alpha=1/10)+
  geom_smooth(method = "lm", formula = y ~ splines::bs(x, 3), se = FALSE)+
  facet_wrap(~Group)+
  NULL
```

#### 2.all.mice.theta
* Centre theta \n

```{r, cache=T}
all.mice.theta %>% 
  ggplot(aes(Group,theta.C))+
  geom_violin(aes(fill=Group),alpha=1/2)+
  # geom_point(aes(color=ID),alpha=1/10)+
  # facet_wrap(~Group)+
  theme_bw()+
  theme(legend.position='none')
  NULL

all.mice.theta %>% 
  ggplot(aes(Group,theta.C))+
  geom_violin(aes(fill=ID),alpha=1/2)+
  # geom_point(aes(color=ID),alpha=1/10)+
  # facet_wrap(~Group)+
  theme_bw()+
  NULL
```

* Tail theta  \n

```{r, cache=T}
all.mice.theta %>% 
  ggplot(aes(Group,theta.T))+
  geom_boxplot(aes(fill=Group),alpha=1/2)+
  # geom_point(aes(color=ID),alpha=1/10)+
  # facet_wrap(~Group)+
  theme_bw()+
  NULL  
all.mice.theta %>% 
  ggplot(aes(theta.C,theta.T))+
  geom_boxplot(aes(fill=ID),alpha=1/2)+
  # geom_point(aes(color=ID),alpha=1/10)+
   facet_wrap(~Group)+
  theme_bw()+
  NULL 

```

#### 3.all.mice.average.vel
* mean velocity \n

```{r, cache=T}
 all.mice.average.vel%>% 
  ggplot(aes(Point,mean.velocity))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  facet_wrap(~Group)+
  theme_bw()+
  NULL


```

* theta tail variance \n

```{r, cache=T}
all.mice.average.vel %>% 
  ggplot(aes(Group,var.angle.T))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  # facet_wrap(~Group)+
  theme_bw()+
  NULL
```

* madien Y \n

```{r, cache=T}
all.mice.average.vel%>% 
  ggplot(aes(Point,madY))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  facet_wrap(~Group)+
  theme_bw()+
  NULL
```

#### 4. all.mice.segment.vel

* velocity \n

```{r, cache=T}
all.mice.segment.vel %>% 
  # filter(Group=='WTUT')%>%  
  ggplot(aes(Point,vel))+
  coord_cartesian(ylim = c(0,1000))+
  geom_boxplot()+
  geom_point(aes(color=ID))+
  facet_wrap(~Group)+
NULL

all.mice.segment.vel %>%filter(Point=='Centre') %>%  
  ggplot(aes(vel))+
  geom_histogram()+
  facet_wrap(~Group)+
  xlim(NA,3000)+
  theme_bw()+
  NULL
```

* insights :
i. dynamic capture from madY and vel
ii. theta (centre/tail) within group: 
    the range of WTUT is narrow, while the range of NPCTG is wide 

## 2. Time series analysis 
### Data explory
#### 1. X,Y 
```{r, cache=T}
library(xts)
library(zoo)
p <- all.mice.theta %>% filter(ID.RUN=='WTUT292.2eRUN1',Point=='Centre') %>% ggplot(aes(x=X,y=Y))+
  geom_line()+
  ggtitle('WTUT292.2eRUN1')+
  theme_bw()+
  transition_reveal(t)+
  NULL
animate(p,renderer = gifski_renderer())

WTUT292.2eRUN1.xts <- all.mice.theta %>% filter(ID.RUN=='WTUT292.2eRUN1',Point=='Centre') %>% select(t,X,Y,theta.C,theta.T)
options(digits.sec=4)
WTUT292.2eRUN1.xts$t <- seq.POSIXt(from=as.POSIXct('1970-01-01 00:00:00'),by = 0.01,length.out = length(WTUT292.2eRUN1.xts$t))
head(WTUT292.2eRUN1.xts)
WTUT292.2eRUN1.xts <- xts(x=WTUT292.2eRUN1.xts[,2:5],order.by=WTUT292.2eRUN1.xts$t)
plot.zoo(WTUT292.2eRUN1.xts)

```

* in each group 
```{r, cache=T}
library(gridExtra)
a <- all.mice.theta %>% filter(Group=='WTUT',Point=='Centre') %>% 
  ggplot(aes(x=t,y=X,col=ID.RUN))+
  geom_line()+
  ggtitle('WTUT')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-300, 300),xlim=c(0,5)) +
  theme(legend.position = "none")+
  NULL
b <- all.mice.theta %>% filter(Group=='NPCTG',Point=='Centre')  %>% 
  ggplot(aes(x=t,y=X,col=ID.RUN))+
  geom_line()+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-300, 300),xlim=c(0,5)) +
  ggtitle('NPCTG')+
  theme(legend.position = "none")+
  NULL
c <- all.mice.theta %>% filter(Group=='NPCUT',Point=='Centre')  %>% 
  ggplot(aes(x=t,y=X,col=ID.RUN))+
  geom_line()+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-300, 300),xlim=c(0,5)) +
  ggtitle('NPCUT')+
  theme(legend.position = "none")+
  NULL
grid.arrange(a,b,c,nrow=1)

```


```{r, cache=T}
a <- all.mice.theta %>% filter(Group=='WTUT',Point=='Centre') %>% 
  ggplot(aes(x=t,y=Y,col=ID.RUN))+
  geom_line()+
  ggtitle('WTUT')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-25, 30),xlim = c(0,5)) +
  theme(legend.position = "none")+
  NULL
b <- all.mice.theta %>% filter(Group=='NPCTG',Point=='Centre')  %>% 
  ggplot(aes(x=t,y=Y,col=ID.RUN))+
  geom_line()+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-25, 30),xlim = c(0,5)) +
  ggtitle('NPCTG')+
  theme(legend.position = "none")+
  NULL
c <- all.mice.theta %>% filter(Group=='NPCUT',Point=='Centre')  %>% 
  ggplot(aes(x=t,y=Y,col=ID.RUN))+
  geom_line()+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-25, 30),xlim = c(0,5)) +
  ggtitle('NPCUT')+
  theme(legend.position = "none")+
  NULL
grid.arrange(a,b,c,nrow=1)
```


```{r, cache=T}
a <- all.mice.theta %>% filter(Group=='WTUT',Point=='Centre') %>% 
  ggplot(aes(x=t,y=theta.T,col=ID.RUN))+
  geom_line()+
  ggtitle('WTUT')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-0.7,0.7),xlim = c(0,5)) +
  theme(legend.position = "none")+
  NULL
b <- all.mice.theta %>% filter(Group=='NPCTG',Point=='Centre')  %>% 
  ggplot(aes(x=t,y=theta.T,col=ID.RUN))+
  geom_line()+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-0.7,0.7),xlim = c(0,5)) +
  ggtitle('NPCTG')+
  theme(legend.position = "none")+
  NULL
c <- all.mice.theta %>% filter(Group=='NPCUT',Point=='Centre')  %>% 
  ggplot(aes(x=t,y=theta.T,col=ID.RUN))+
  geom_line()+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-0.7,0.7),xlim = c(0,5)) +
  ggtitle('NPCUT')+
  theme(legend.position = "none")+
  NULL
grid.arrange(a,b,c,nrow=1)
```


```{r, cache=T}
a <- all.mice.theta %>% filter(Group=='WTUT',Point=='Centre') %>% 
  ggplot(aes(x=t,y=theta.C,col=ID.RUN))+
  geom_line()+
  ggtitle('WTUT')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-0.7,0.7),xlim = c(0,5)) +
  theme(legend.position = "none")+
  NULL
b <- all.mice.theta %>% filter(Group=='NPCTG',Point=='Centre')  %>% 
  ggplot(aes(x=t,y=theta.C,col=ID.RUN))+
  geom_line()+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-0.7,0.7),xlim = c(0,5)) +
  ggtitle('NPCTG')+
  theme(legend.position = "none")+
  NULL
c <- all.mice.theta %>% filter(Group=='NPCUT',Point=='Centre')  %>% 
  ggplot(aes(x=t,y=theta.C,col=ID.RUN))+
  geom_line()+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-0.7,0.7),xlim = c(0,5)) +
  ggtitle('NPCUT')+
  theme(legend.position = "none")+
  NULL
grid.arrange(a,b,c,nrow=1)
```

```{r, cache=T}
a <- all.mice.theta %>% filter(ID=='WTUT292.2e',Point=='Head',Run %in% c('RUN1','RUN2','RUN3')) %>% 
  ggplot(aes(x=t,y=Y,col=Run))+
  geom_line()+
  ggtitle('WTUT292.2e-Y')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-30,30),xlim = c(0,3)) +
  theme(legend.position = "none")+
  NULL
b <- all.mice.theta %>% filter(ID=='WTUT292.2e',Point=='Head',Run %in% c('RUN1','RUN2','RUN3')) %>% 
  ggplot(aes(x=t,y=theta.C,col=Run))+
  geom_line()+
  ggtitle('WTUT292.2e-theta.C')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-0.5,0.5),xlim = c(0,3)) +
  theme(legend.position = "none")+
  NULL
c <- all.mice.theta %>% filter(ID=='WTUT292.2e',Point=='Head',Run %in% c('RUN1','RUN2','RUN3')) %>% 
  ggplot(aes(x=t,y=theta.T,col=Run))+
  geom_line()+
  ggtitle('WTUT292.2e-theta.T')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-0.5,0.5),xlim = c(0,3)) +
  theme(legend.position = "none")+
  NULL
grid.arrange(a,b,c,nrow=1)
```

```{r}
library(gridExtra)
a <- all.mice.theta %>% 
  filter(ID=='NPCUT293.2c',Point=='Head',Run %in% c('RUN3','RUN7','RUN11')) %>% 
  ggplot(aes(x=t,y=Y,col=Run))+
  geom_line()+
  ggtitle('NPCUT293.2c-Y')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-30,30),xlim = c(0,3)) +
  theme(legend.position = "none")+
  NULL
b <- all.mice.theta %>% 
  filter(ID=='NPCUT293.2c',Point=='Head',Run %in% c('RUN3','RUN7','RUN11')) %>% 
  ggplot(aes(x=t,y=theta.C,col=Run))+
  geom_line()+
  ggtitle('NPCUT293.2c-theta.C')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-0.5,0.5),xlim = c(0,3)) +
  theme(legend.position = "none")+
  NULL
c <- all.mice.theta %>% filter(ID=='NPCUT293.2c',Point=='Head',Run %in% c('RUN3','RUN7','RUN11')) %>% 
  ggplot(aes(x=t,y=theta.T,col=Run))+
  geom_line()+
  ggtitle('NPCUT293.2c-theta.T')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-0.5,0.5),xlim = c(0,3)) +
  theme(legend.position = "none")+
  NULL
grid.arrange(a,b,c,nrow=1)

```

```{r}
a <- all.mice.theta %>% filter(ID=='NPCTG294.2c',Point=='Head',Run %in% c('RUN1','RUN2','RUN3')) %>% 
  ggplot(aes(x=t,y=Y,col=Run))+
  geom_line()+
  ggtitle('NPCTG294.2c-Y')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-30,30),xlim = c(0,3)) +
  theme(legend.position = "none")+
  NULL
b <- all.mice.theta %>% filter(ID=='NPCTG294.2c',Point=='Head',Run %in% c('RUN1','RUN2','RUN3')) %>% 
  ggplot(aes(x=t,y=theta.C,col=Run))+
  geom_line()+
  ggtitle('NPCTG294.2c-theta.C')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-0.5,0.5),xlim = c(0,3)) +
  theme(legend.position = "none")+
  NULL
c <- all.mice.theta %>% filter(ID=='NPCTG294.2c',Point=='Head',Run %in% c('RUN1','RUN2','RUN3')) %>% 
  ggplot(aes(x=t,y=theta.T,col=Run))+
  geom_line()+
  ggtitle('NPCTG294.2c-theta.T')+
  scale_x_continuous(breaks = seq(0, 5, 1)) +
  coord_cartesian(ylim = c(-0.5,0.5),xlim = c(0,3)) +
  theme(legend.position = "none")+
  NULL
grid.arrange(a,b,c,nrow=1)
```

* WTUT VS NPCTF VS NPCUT

```{r}
library(xts)
WTUT292.2eRUN1.xts <- all.mice.theta %>% filter(ID.RUN=='WTUT292.2eRUN1',Point=='Centre') %>% select(t,X,Y,theta.C,theta.T)
options(digits.sec=4)
WTUT292.2eRUN1.xts$t <- seq.POSIXt(from=as.POSIXct('1970-01-01 00:00:00'),by = 0.01,length.out = length(WTUT292.2eRUN1.xts$t))
# head(WTUT292.2eRUN1.xts)
WTUT292.2eRUN1.xts <- xts(x=WTUT292.2eRUN1.xts[,2:5],order.by=WTUT292.2eRUN1.xts$t)
attr(WTUT292.2eRUN1.xts,'frequency') <-60
# frequency(WTUT292.2eRUN1.xts)

NPCTG286.1gRUN1.xts <- all.mice.theta %>% filter(ID.RUN=='NPCTG286.1gRUN1',Point=='Centre') %>% select(t,X,Y,theta.C,theta.T)
options(digits.sec=4)
NPCTG286.1gRUN1.xts$t <- seq.POSIXt(from=as.POSIXct('1970-01-01 00:00:00'),by = 0.01,length.out = length(NPCTG286.1gRUN1.xts$t))
# head(WTUT292.2eRUN1.xts)
NPCTG286.1gRUN1.xts <- xts(x=NPCTG286.1gRUN1.xts[,2:5],order.by=NPCTG286.1gRUN1.xts$t)
attr(NPCTG286.1gRUN1.xts,'frequency') <-60


NPCUT293.2cRUN11.xts <- all.mice.theta %>% filter(ID.RUN=='NPCUT293.2cRUN11',Point=='Centre') %>% select(t,X,Y,theta.C,theta.T)
options(digits.sec=4)
NPCUT293.2cRUN11.xts$t <- seq.POSIXt(from=as.POSIXct('1970-01-01 00:00:00'),by = 0.01,length.out = length(NPCUT293.2cRUN11.xts$t))
# head(WTUT292.2eRUN1.xts)
NPCUT293.2cRUN11.xts <- xts(x=NPCUT293.2cRUN11.xts[,2:5],order.by=NPCUT293.2cRUN11.xts$t)
attr(NPCUT293.2cRUN11.xts,'frequency') <-60




all.xts <- merge.xts(WTUT=WTUT292.2eRUN1.xts,
                     NPCTG=NPCTG286.1gRUN1.xts,
                     NPCUT=NPCUT293.2cRUN11.xts,
                     all=c(TRUE,TRUE,TRUE))

plot.zoo(all.xts,plot.type = 'multiple',nc=3)

```



```{r}

paste0('WTUT-Y')
plot(decompose(as.ts(WTUT292.2eRUN1.xts$Y)))
paste0('NPCTG-Y')
plot(decompose(as.ts(NPCTG286.1gRUN1.xts$Y)))
paste0('NPCUT-Y')
plot(decompose(as.ts(NPCUT293.2cRUN11.xts$Y)))

```

*ARIMA model

```{r}
par(mfrow=c(1,2))
acf(as.ts(WTUT292.2eRUN1.xts$Y))
pacf(as.ts(WTUT292.2eRUN1.xts$Y))

wtut.md <- auto.arima(as.ts(WTUT292.2eRUN1.xts$Y))
wtut.md

checkresiduals(wtut.md)
wtut.md.sim <- arima.sim(model = list(order=c(0,1,2),ma=c(-0.083,0.4)),n=500) 
plot(wtut.md.sim)

```


```{r}
par(mfrow=c(1,2))
acf(as.ts(NPCUT293.2cRUN11.xts$Y))
pacf(as.ts(NPCUT293.2cRUN11.xts$Y))

NPCUT.md <- auto.arima(as.ts(NPCUT293.2cRUN11.xts$Y))
NPCUT.md

checkresiduals(NPCUT.md)
NPCUT.md.sim <- arima.sim(model = list(order=c(1,1,1),ar=0.66,ma=-0.4),n=500) 
plot(NPCUT.md.sim)
```

* Models testing

```{r}
WTUT292.2eRUN2.ts <- all.mice.theta %>% filter(ID.RUN=='WTUT292.2eRUN2',Point=='Centre') %>% select(t,Y)
options(digits.sec=4)
WTUT292.2eRUN2.ts <- as.ts(x=WTUT292.2eRUN2.ts[,2],order.by=WTUT292.2eRUN2.ts$t)


NPCUT293.2cRUN7.ts <- all.mice.theta %>% filter(ID.RUN=='NPCUT293.2cRUN7',Point=='Centre') %>% select(t,Y)
options(digits.sec=4)
NPCUT293.2cRUN7.ts<- as.ts(x=NPCUT293.2cRUN7.ts[,2],order.by=NPCUT293.2cRUN7.ts$t)


paste0('wtut.md')
wtut.md <- auto.arima(as.ts(WTUT292.2eRUN1.xts$Y))
fc.wtut.md.wt <- forecast(wtut.md,h=length(WTUT292.2eRUN2.ts))
fc.wtut.md.npc <- forecast(wtut.md,h=length(NPCUT293.2cRUN7.ts))
fc.wtut.tg <- forecast(wtut.md,h=length(NPCTG286.1gRUN1.xts$Y))
knitr::kable(accuracy(fc.wtut.md.wt,WTUT292.2eRUN2.ts))
knitr::kable(accuracy(fc.wtut.md.npc,NPCUT293.2cRUN7.ts))
knitr::kable(accuracy(fc.wtut.tg,as.ts(NPCTG286.1gRUN1.xts$Y)))

paste0('npc.md')
NPCUT.md <- auto.arima(as.ts(NPCUT293.2cRUN11.xts$Y))
fc.npc.md.wt <- forecast(NPCUT.md,h=length(WTUT292.2eRUN2.ts))
fc.npc.md.npc <- forecast(NPCUT.md,h=length(NPCUT293.2cRUN7.ts))
fc.npc.tg <- forecast(NPCUT.md,h=length(NPCTG286.1gRUN1.xts$Y))
knitr::kable(accuracy(fc.npc.md.wt,WTUT292.2eRUN2.ts))
knitr::kable(accuracy(fc.npc.md.npc,NPCUT293.2cRUN7.ts))
knitr::kable(accuracy(fc.npc.tg,as.ts(NPCTG286.1gRUN1.xts$Y)))



```



